% Shree KRISHNAya Namaha
\documentclass{article}
\title{Finance Manager Android App - Versions log}
\author{Nagabhushan S N}
\usepackage[a4paper,margin=1in,footskip=0.25in]{geometry}
\usepackage{hyperref}
\hypersetup {
colorlinks = true,
linkcolor = black
}

\begin{document}
    \maketitle
    \tableofcontents
    \newpage

    \section{v4.0.7 (114)}\label{sec:114}
    \begin{itemize}
        \item Double Back Press to exit App
        \item Bug Fix: In AutoRestore in Splash Activity, newly added fields such as hidden and deleted are not checked.
        As a result, if there is data corruption of those fields, it is not recovered - Fixed
    \end{itemize}

    \section{v4.0.8 (115)}\label{sec:115}
    \begin{itemize}
        \item Bug Fix: When a transaction is edited, it will be deleted and added at the bottom in database.
        But in TransactionsActivity, it will be edited at the displayed position.
        As a result, when it is edited again, the next transaction will be edited - Fixed
        \item Toast Texts removed in BackupManager.
        Instead, return values are used.
        \item AutoBackup takes considerable amount if time when Data is huge.
        As a result, App won't be closed as soon as double-back is pressed.
        To overcome it, AutoBackup will be done in a separate thread insted of UI Thread.
        So. App will be closed immediately
    \end{itemize}

    \section{v4.1.0 (116)}\label{sec:116}
    \begin{itemize}
        \item A new method getTransactions() is created in DatabaseAdapter that takes filterRules, hiddenTransactions, offset and numTransactions as parameters.
        filterRules is an ArrayList of Strings.
        Not defined how to use yet.
        It returns 'numTractions' number of transactions from bottom with given offset.
        \item TransactionsActivity buildLayout updated to display last 100 transactions by default
        \item Show More button added which when clicked displays 100 more transactions
    \end{itemize}

    \section{v4.1.1 (117)}\label{sec:117}
    \begin{itemize}
        \item Created a custom view "ExpandCollapseItem" which is used in Filtering Transactions
        \item FilterActivity created that lets user filter transactions by date, transaction type, wallets/banks and a search keyword
        \item Bug Fix: While editing transactions, in DatabaseAdapter, transactionType was not updated - Fixed.
        \item While displaying particulars in TransactionsActivity, wallets/banks will be prefixed
        \item For build version, in SplashActivity, app icon will be displayed instead of Krishna Photo.
        Also, "Shree KRISHNAya Namaha" will be hidden
        \item In TransactionsActivity, while displaying particulars, source/destination (Wallet/Bank) will be displayed and particular on next line
    \end{itemize}

    \section{v4.1.2 (118)}\label{sec:118}
    \begin{itemize}
        \item Bug Fix: In TransactionsActivity, after adding a transaction, if that transaction is edited or deleted, instead of selecting that Transaction, some other Transaction was getting selected.
        Earlier, contextMenuTransactionNo field was used to get transactions and all.
        Now, for each transactionLayout, a tag of the format "yyyy-id" (Eg: 2017-123) will be set and this tag is used to retrieve transactions as well as layouts
    \end{itemize}

    \section{v4.1.3 (119)}\label{sec:119}
    \begin{itemize}
        \item Bug Fix: When restoring data, selecting the backup file from default File Explorer doesn't used to work.
        Selecting the file from ES File Explorer used to work.
        Now, it works with default File Explorer also.
        \item Few more quotes added
    \end{itemize}

    \section{v4.2.0 (120)}\label{sec:120}
    \begin{itemize}
        \item Git Integration added
        \item Change Log Added
    \end{itemize}

    \section{v4.2.1 (121)}\label{sec:121}
    \begin{itemize}
        \item .gitignore updated to exclude non source code files
        \item All files deleted except source code and some gradle settings.
        If any required file is found missing, please refer to files of previous version i.e.\ v4.2.0(120)
    \end{itemize}

    \section{v4.2.2 (122)}\label{sec:122}
    \begin{itemize}
        \item .gitignore updated to exclude remaining non source code files
    \end{itemize}

    \section{v4.2.3 (123)}\label{sec:123}
    \begin{itemize}
        \item .gitignore generated from .gitignore plugin.
        Now, only recommended files are ignored.
        \item Some files which were wrongly removed in v4.2.1 added back to GIT
    \end{itemize}

    \section{v4.3.0 (124)}\label{sec:124}
    \begin{itemize}
        \item Option to include or exclude the transaction in counters added
        \item Bug Fix: While displaying templates (auto-complete) for Transfer Transactions, Income Templates were retrived - Fixed.
        \item Bug Fix: When opening TransactionsActivity, if the number of transactions to be shown is less than 50
        \item Removed unused commented code in DatabaseManager.java
        \item Old Backup reader methods in RestoreManager.java, which were not used and commented have been removed
        \item WalletSetupFragment.java class, which is not used anymore has been removed
    \end{itemize}

    \section{v4.3.1 (125)}\label{sec:125}
    \begin{itemize}
        \item Few Code improvements suggested by Android Studio
        \item IncludeInCounters changed to ExcludeFromCounters only in frontend.
        In backend, it is still IncludeInCounters
        \item Backing up data will be done in a separate thread.
        UI will no more hang due to huge data.
        Backup result will also be displayed.
        \item Text centered vertically in IndefiniteWaitDialogs
        \item Daily Backup Added.
        It can be enabled or disabled from Settings. (Beta)
        \item APP\_VERSION\_NO constants moved from SplashActivity to Constants class
        \item SharedPreferences Key constants moved from SplashActivity to Constants class
        \item Manual Backup and Daily Backup return result now instead of void
        \item Flow Logging added for Daily Backup Code
    \end{itemize}

    \section{v4.3.2 (126)}\label{sec:126}
    \begin{itemize}
        \item Fixed a potential bug in retrieving time.
        Earlier time was retrieved in 12-hr format and no am/pm was stored.
        Now time is retrieved in 24-hr format.
        \item Change Log file formatted.
        \item App released.
    \end{itemize}

    \section{v4.3.3 (127)}\label{sec:127}
    \begin{itemize}
        \item FilterActivity.java renamed to TransactionsFilterActivtity.java
        \item activity\_filter.xml renamed to activity\_filter\_transactions.xml
        \item Added basic filtering by year in StatisticsActivity
    \end{itemize}

    \section{v4.3.4 (128)}\label{sec:128}
    \begin{itemize}
        \item Bug Fix: App used to crash while selecting a template which contains a single quote in particulars due to error in SQLite Query.
    \end{itemize}

    \section{v4.3.5 (129)}\label{sec:129}
    \begin{itemize}
        \item Bug Fix: When editing a Bank, if the name is unchanged, it used to prompt for changing name - Fixed.
        \item Gradle upgraded to 3.0.1
    \end{itemize}

    \section{v4.3.6 (130)}\label{sec:130}
    \begin{itemize}
        \item MinSdkVersion changed to 16
        \item TargetSdkVersion changed to 24
        \item com.chaturvedi.datastructures package created.
        \item Month enum added in com.chaturvedi.datastructures package
        \item Date and Time classes moved from com.chaturvedi.financemanager.datastructures package to com.chaturvedi.datastructures
        \item IntervalSelector custom widget added in com.chaturvedi.customviews
        \item ExportActivity Added.
        Data of any interval can be exported.
        \item Added few utility methods in DatabaseAdapter.
        \item The generic getTransactions() method in DatabaseAdaptor has been deprecated.
        A similar method is added which uses Date objects instead of Strings for start and end dates.
        \item isLeapYear() method added in com.chaturvedi.datastructures.Date class
        \item Export folder changed to "Android/Chaturvedi/Finance Manager"
        \item Minor bug fixes and enhancements
    \end{itemize}

    \section{v4.3.7 (131)}\label{sec:131}
    \begin{itemize}
        \item IndefiniteWaitDialog renamed to IndefiniteWaitDialogBuilder
        \item ProgressiveWaitDialogBuilder added
        \item export package created in com.chaturvedi.financemanager.extras
        \item Exporting to PDF added.
        IText library added.
        \item PdfExportManager and HtmlExportManager added.
        \item Exporting will be done in background thread.
        Progress will be shown on a dialog
        \item Few Exporting Preferences will be saved and restored when ExportActivity is reopened
        \item UI improvement in SummaryActivity.
        MarginTop set to 5\% of screen height
        \item Bug Fix: App used to crash when transferring from Bank to Bank - Fixed.
        \item App released.
    \end{itemize}

    \section{v4.3.8 (132)}\label{sec:132}
    \begin{itemize}
        \item Update125to131 which was missing in previous release added.
        \item Toast message saying the app is updating will be displayed from SplashActivity instead of individual classes
        \item HintAdapter custom class added in com.chaturvedi.customviews.
        Shows "Select" at first and it will disappear once a selection is made
        \item IncomeLayout, ExpenseLayout and TransferLayout updated to use HintAdapter
    \end{itemize}

    \section{v4.3.9 (133)}\label{sec:133}
    \begin{itemize}
        \item Added support to restore deleted wallets and banks
        \item Multiple bug fixes related to deleting wallets or banks
        \item menu\_statistics renamed to activity\_statistics in res/menu/ folder
    \end{itemize}

    \section{v4.4.0 (134)}\label{sec:134}
    \begin{itemize}
        \item Removed instruction in EditExpTypesActivity
        \item Added support to restore deleted Expenditure Types
        \item Bug Fix: Earlier, after opening EditWallets/BanksActivity, deleted items used to be displayed - Fixed.
        \item In Edit Activities, deleted items will be displayed in gray colour
        \item FAQs updated (Removed stale and irrelevant FAQs)
        \item Added Update131to134 class
        \item App released.
    \end{itemize}

    \section{v4.4.1 (135)}\label{sec:135}
    \begin{itemize}
        \item Release.log added
        \item 'Change Log.txt' renamed to Change.log
        \item Bug Fix in DatabaseAdapter getTransactions() deprecated method
        \item All instances of getTransactions() deprecated method replaced with newer version
        \item UpdateClasses with no updates deleted (88to89, 125to131, 131to134)
        \item App released.
    \end{itemize}

    \section{v4.4.2 (136)}\label{sec:136}
    \begin{itemize}
        \item Project ported to Android Studio 3.4
        \item SD Read and Write permissions will be asked at run time
        \item Reading Bank SMS functionality disabled (commented)
        \item minSdkVersion: 21
        \item targetSdkVersion: 28
        \item \textit{Change.log} moved to \textit{MyResources/ChangeLog/ChangeLog.tex}
        \item \textit{Release.log} moved to \textit{MyReources/ReleasedApps/Release.log}
        \item All released apps till date added in folder \textit{MyResources/ReleasedApps/}
        \item AboutActivity updated
    \end{itemize}


    \section{v4.4.3 (137)}\label{sec:137}
    \begin{itemize}
        \item Project ported to Android Studio 3.6.3
        \item Sorting transactions added (TransactionsActivity and ExportActivity)
        \item Project ported to Android Studio 4.2.2
        \item When exporting a month, default filename changed to prepend year and month number at the beginning.
        This helps in automatic sorting of exports in filesystem.
        \item Default Value for Automatic Backup and Restore setting changed from "Automatic Backup and Restore" to "Automatic Backup".
    \end{itemize}


    \section{v4.4.4 (138)}\label{sec:138}
    \begin{itemize}
        \item Project ported to Android Studio 2020.3.1 Patch 2.
        \item Backup and Export updated to save files in Documents folder instead of Android folder.
    \end{itemize}
\end{document}